Online {\IterComp}

### 2017-09-16 abstract.tex
fix values

    Our online iterative compilation method yields programs that get 80\% of the speedup achievable by an offline oracle,
    but without executing any input more than once, which the oracle cannot do.
    Through probe removal we bring the instrumentation overhead down to only 5\% on average, making our
    approach suitable for real-world scenarios. %We show practical online iterative compilation for the first time,
    %optimizing programs according to the range of inputs users actually present.
\end{abstract}

>>>>

    Our online iterative compilation method yields programs that get 60\% of the speedup achievable by an offline oracle,
    but without executing any input more than once, which the oracle cannot do.
    Through probe removal we bring the instrumentation overhead down to only 5\% on average, making our
    approach suitable for real-world scenarios. %We show practical online iterative compilation for the first time,
    %optimizing programs according to the range of inputs users actually present.
\end{abstract}

### 2017-09-16 conclusions.tex
fix values

We use this efficiency metric to enable for the first time true online iterative compilation. Instead of comparing different optimizations
sequences offline by running the application repeatedly with different optimizations applied but the same input, we can now compare runs
using different inputs as they are provided by the user. We evaluated our online iterative compilation methodology using the KDataSets
benchmark suite. Experimental results show that we deliver \red{80\%} of the speedup achieved by an offline oracle while not having to
execute any input more than once. Our probe optimization and removal strategies bring the instrumentation overhead down to only \red{4\%}
on average, making our approach suitable for integration into software products.

>>>>

We use this efficiency metric to enable for the first time true online iterative compilation. Instead of comparing different optimizations
sequences offline by running the application repeatedly with different optimizations applied but the same input, we can now compare runs
using different inputs as they are provided by the user. We evaluated our online iterative compilation methodology using the KDataSets
benchmark suite. Experimental results show that we deliver 60\% of the speedup achieved by an offline oracle while not having to
execute any input more than once. Our probe optimization and removal strategies bring the instrumentation overhead down to only 5\%
on average, making our approach suitable for integration into software products.
